Supplementary Material

### 2019-04-24 eDriversMS-SI-v2.rmd
latest version of the manuscript

---
title: Supplementary Material
fontsize: 12pt
output:
  pdf_document:
    toc: false
    number_sections: true
  html_document:
    number_sections: true
relativeurls: true
bibliography: eDriversMS.bib
csl: frontiers.csl
link-citations: yes
---

<!--
cd phdproj/edrivers/edriversms
rmarkdown::render('./eDriversMS-SI.rmd', 'pdf_document')
rmarkdown::render('./eDriversMS-SI.rmd', 'html_document')
-->

@@

### Aragonite

***Describe data***

We interpolated aragonite distribution using the exponential kriging model.
We then built an index of aragonite level stress. When $\Omega$ aragonite levels
decrease below 1, the water becomes corrosive to calcifying organisms such as
echinoderms, corals and mollusks larvae. These organisms thus have to
continually recalcify their shells to maintain their structure, which becomes
harder to do as $\Omega$ aragonite levels further decrease towards 0. We therefore
considered stress associated to decreasing $\Omega$ aragonite levels to increase
linearly between values of 1 and 0. The index of stress therefore has a value of
0 and 1 for values of $\Omega$ aragonite equal to 1 and 0, respectively.

@@

***Describe data***

We interpolated the dissolved oxygen using cokriging with depth as a covariable,
as done in [@dutil2011]. According to @diaz1995, severe hypoxia can be observed
when oxygen saturation falls below 2 $ml$ $L^{-1}$ or 62.5 $\mu mol$ $L^{-1}$, which is considered
the level necessary to maintain most animal life. This threshold is equal to 1.4
$ml$ $L^{-1}$ (1 $mg$ $L^{-1}$ = 0.7 $ml$ $L^{-1}$).
We used this threshold to create an index of hypoxia using an inverted logistic curve
to transform the dissolved oxygen values as an index of hypoxic stress $H_s$ ranging
from 0 to 1, under the assumption that hypoxic stress will increase following
a logistic curve as it approaches the hypoxic threshold:

$$H_s = \frac{-1}{200 * e^{-2.5 * DO_2}} + 1$$

@@

The data used to characterize bottom temperature anomalies come from the
Department of Fisheries and Oceans’ (DFO) Atlantic Zone Monitoring Program
[AZMP; @galbraith2018]. We provide a brief summary of data and methods
to characterize surface temperature climatology and anomalies in this document.
For more details, refer to @galbraith2018.

Bottom temperatures are interpolated in the Gulf using
conductivity-temperature-depth (CTD) sampling performed annually through DFO's
multispecies surveys for the northern Gulf in August and for the Magdalen
Shallows in September. Using this sampling survey, temperatures are interpolated
at each 1 m depth layer on a 2 km resolution grid. Bottom temperature are then
extracted from this grid by using a bathymetry layer from the Canadian
Hydrographic Survey [@dutil2012].

We used temperature anomalies, *i.e.* deviations from long-term normal conditions,
to measure an annual index of stress associated with extreme temperatures between
2013 and 2017. Temperature anomalies were calculated using the difference between
grid cell monthly climatologies to the associated long-term averages generated
from the reference period between 1981 and 2010. Grid cells whose monthly value
exceeded ±0.5 standard deviation (SD) from the long-term average were considered
as anomalous [@galbraith2018].

Outliers in the data were considered as those that fell beyond the
interquartile range (IQR) * 3, identified as extreme ouliers by @tukey1977.
Outlier values were capped to correspond to the 5th and 95th percentiles.
Anomalies were divided into positive and negative anomalies and
summed for the available months of September and August.
By adding the monthly anomaly values, we essentially considered the summed
deviation from the mean as an indicator of the annual intensity of surface
temperature anomalies in the St. Lawrence.

@@

The data used to characterize surface temperature anomalies come from the
Department of Fisheries and Oceans’ (DFO) Atlantic Zone Monitoring Program
[AZMP; @galbraith2018]. We provide a brief summary of data and methods
to characterize surface temperature climatology and anomalies in this document.
For more details, refer to @galbraith2018.

The surface layer is characterized using a variety of methods:

1. Temperature-salinity sensors installed on various sihps and forming the
shipboard thermosalinograph network,
2. Moored instruments recording water temperature every 30 minutes and forming
the thermograph network,
3. Sea surface temperature (SST) monthly composite climatologies using Advanced
Very High Resolution Radiometer (AVHRR) satellite images from the National
Oceanic and Atmospheric Administration (NOAA) and European Organisation for the
Exploitation of Meteorological Satellites (EUMETSAT) available from the Maurice
Lamontagne Institute sea surface temperature processing facility at a 1km
resolution from 1985-2013 and from the Bedford Institute of Oceanography (BIO)
Operational Remote Sensing group at a 1.5km resolution since 2014.

Positive and negative surface temperature anomalies were identified following
the same approach used for bottom temperature anomalies. Compared to the
bottom temperature anomalies, however, data is available thoughout the year.
Only the months of April to November were included to avoid biases associated
with anomalies measurements due to the presence of ice cover.

@@

- Coastal development
- Direct human impact
- All fisheries data
- Hypoxia
- Inorganic pollution
- Invasive species
- Nutrient pollution
- Organic pollution
- Sea bottom temperature anomalies
- Shipping

@@

![Frequency distribution of the untransformed data for all driver layers. \label{hist}](./figures/drHist.png)

![Distribution and intensity of transformed and normalized drivers in the Estuary and Gulf of St. Lawrence available on *eDrivers*. \label{drivers}](./figures/drivers.png)

\newpage

@@

![Frequency distribution of cumulative exposure (*i.e.* sum of normalized driver intensity in each grid cell) and percent contribution of each driver to the frequency distribution of cumulative exposure in the Estuary and Gulf of St. Lawrence \label{marimekko}](./figures/marimekko.png)

@@

We identified regions with similar cumulative exposure regimes, referred to as
threat complexes after [@bowler2019], using a partional *k-medoids* clustering
algorithm, CLARA [CLustering for Large Applications; @kaufman1990], which was
designed to use with large datasets. The CLARA algorithm uses the PAM
(Partition Around Medoids) algorithm on a sample from the original dataset
to identify a set of $k$ objects that are representative of all other objects,
*i.e.* medoids (also referred to as examplars) and that are central to the
cluster they represent. The goal of the algorithm is to iteratively minimize
dissimilarity between objects in the cluster and the representative medoid.
Sets of $k$ medoids are thus selected and replaced in order to iteratively
minimize the intra-cluster dissimilarity. With the CLARA algorithm, this
process is repeated and iterations are compared on the basis of their average
dissimilarity between objects and cluster medoids to select the optimal set of
$k$ medoids that minimizes average dissimilarity. We performed the analyses for
a total of 100 iterations using samples of 10000 observations, representing ~5%
of the drivers dataset. Analyses were performed using the *cluster* R package
[@maechler2018].

Because the algorithm identifies clusters by minimizing dissimilarity around a
set of *k* medoids, it requires a pre-defined number of clusters. The
appropriate number of clusters $k$ was thus tested using values ranging from
2 to 10 and validated by selecting the number of clusters that maximized the average
silhouette width [@kaufman1990] and minimized the total within-cluster sum of
squares (WSS; Figure S\ref{valid}).

We also validated the clustering by comparing *k-medoids* clustering with
*k-means* clustering with the *Lloyd* algorithm [@lloyd1982]. The *k-means*
approach is similar to the *k-medoids*, but identifies observations belonging
to a cluster iteratively by minimizing the mean intra-cluster squared distance
until it converges to an optimal solution. We used 25 random sets and set a
maximum of 1000 iterations for the analysis. Analyses were performed using
the *stats* R package [@rcoreteam2018]. We used the same validation procedure
to select the optimal number of clusters $k$ than with the *k-medoids*
clustering (Figure S\ref{valid}).

Both the *k-medoids* and *k-means* clustering validation procedure suggest that
there are 7 distinc threat complexes in the St. Lawrence (Figure S\ref{valid}).
While the comparison of of the spatial distribution of clusters results in only
a 66% cell correspondance between the *k-medoids* and *k-means* approaches, the
bulk of the difference is attributable to a single undivided cluster that
combines most of the southern and norther Gulf in a single cluster in favor of
a more localised cluster by the *k-means* algorithm (Figure S\ref{comparison}).
While *k-means* algorithms are much faster than *k-medoids* since it does not
need a pairwise dissimilarity measurement of all observations, it is also more
sensitive to outliers since it focuses on the mean rather than a centroid. We
therefore opted the use of *k-medoids* clustering.

![Validation procedure for the *k-medoids* and *k-means* clustering algorithms based on the number of cluster that maximizes average silhouette width [upper panels; @kaufman1990] and minimizes the total within-cluster sum of squares (WSS; lower panels). \label{valid}](./figures/validation.png)

![Comparison of the distribution of the 7 clusters identified using the *k-medoids* and *k-means* clustering algoriths and the percent grid cell correspondance between the two approaches \label{comparison}](./figures/clusterComp.png)

@@

The difference between clusters was explored by measuring the total inter-cluster
dissimilarity and the contribution of each driver to the total inter-cluster
dissimilarity using a similarity percentage analysis (SIMPER) with Bray-Curtis
dissimilarity [Figure S\ref{inter}; @clarke1993]. As the drivers dataset is too
large, we used a bootstrap procedure for the SIMPER analysis, randomly selecting
5% of each cluster to run the analysis and repeating the process over 300 iterations.
We also compared the mean intensity of each driver within each cluster to
better capture the inter-cluster dissimilarity. Analyses were performed using
the *vegan* R package [@oksanen2018].

![Evaluation of inter-cluster dissimilarity using a similarity percentage analysis (SIMPER) with Bray-Curtis dissimilarity [@clarke1993]. The figure diagonal presents the distribution of the 7 clusters identified using the *k-medoids* clustering algorithm. The lower triangle shows all combinations of inter-cluster dissimilarity with circular barplots showing the percent contribution to total dissimilarity of each driver and with the total inter-cluster dissimilarity in the center of the barplots. The upper triangle shows the average relative intensity of each driver for all driver combinations, with barplots to the left and the right representing the row and columns clusters, respectively. \label{inter}](./figures/interDissimilarity.png)

@@

Intra-cluster similarity was evaluated using the Bray-Curtis similarity index
(Figure S\ref{intra}). As with the inter-cluster dissimilarity, we used a
bootstrap procedure for the intra-cluster similarity, randomly selecting 5% of
each cluster observation to run the analysis and repeating the process over 300
iterations. We however did not use the bootstraping procedure for clusters 2
and 6, as they both contain less than 10000 observations, making the calculation
time more manageable.

![Evaluation of intra-cluster similarity using the Bray-Curtis similarity index. The distribution of all 7 clusters is presented along with circular barplots showing the percent contribution to total similarity of each driver and with the total intra-cluster similarity in the center of the barplots. \label{intra}](./figures/intraSimilarity.png)

>>>>

---
title: Supplementary Material
fontsize: 12pt
output:
  pdf_document:
    toc: false
    number_sections: true
  html_document:
    number_sections: true
header-includes:
    - \usepackage{float}
    - \usepackage{setspace}
    - \onehalfspacing
relativeurls: true
bibliography: eDriversMS.bib
csl: frontiers.csl
link-citations: yes
---

<!--
cd phdproj/edrivers/edriversms
rmarkdown::render('./eDriversMS-SI-v2.rmd', 'pdf_document')
rmarkdown::render('./eDriversMS-SI.rmd', 'html_document')
-->

@@

### Acidification

Oceans are the largest reservoir and sink of atmospheric carbon dioxide ($CO_2$). Its uptake
increases seawater acidity and the lowers saturation state with respect to calcite
($\Omega_C$) and aragonite ($\Omega_A$), the two most common $CaCO_3$ polymorphs
constituting the shells and skeleton of many marine organisms [@mucci2017].
This can have deleterious effects on carbonate-secreting organisms (*e.g.* mollusks and crustaceans)
and certain physiological processes in non-calcifying organisms
[@fabry2008; @kroeker2013].

When $\Omega_C$ or $\Omega_A$ decrease below 1, water
becomes undersaturated and corrosive to the skeletal minerals of carbonate-secreting
organisms. Note that if $\Omega_A$ $< 1$, the waters
may still be supersaturated with respect to calcite since it is 50% more soluble
than aragonite. However, organisms
have wide ranging responses to $\Omega_C$ and $\Omega_A$ saturation state.
For example, most corals stop calcifying at $\Omega_A$ $< 2$ [@kleypas2006; @bove2019], while other organisms
may have adapted to precipitate $CaCO_3$ even when seawater is undersaturated
with respect to calcite [$\Omega_C$ $< 1$ or $\Omega_A$ $< 0.65$; e.g. @uthicke2016].

We used $\Omega_{A}$ saturation state to characterize ocean acidification in the
bottom waters of the St. Lawrence. The data were collected [...]. $\Omega_{A}$,
pH, dissolved oxygen ($O_2$) and pressure were sampled at 117 stations in the
Estuary and Gulf of St. Lawrence in the summer of 2018. The majority of sampling
stations were located in the Southern Gulf ($n = 84$), compared to the Estuary
and Northern Gulf ($n = 33$).

To account for low sample size in the Northern Gulf, we used the
correlation between $O_2$ and $CO_2$, which are linked through the stoichiometry
of the respiration reaction in waters that are isolated from the atmosphere [@mucci2011].
Metabolic $CO_2$ increases in
water through biotic processes such microbial respiration of organic matter
[@mucci2011]. In deep waters, variations of $\Omega_{A}$ are largely governed by the addition of metabolic
$CO_2$, whereas near the air-sea interface $O_2$ is replenished faster than $CO_2$ can
escape [@zeebe2001]. The impact of respiration on carbonate chemistry is highest in hypoxic
regions, where metabolic $CO_2$ accumulates to high concentrations [@mucci2011].

We explored the correlation between $\Omega_{A}$ and $O_2$ in the data and
found no significant correlation at the scale of the whole St. Lawrence (*p-value*:
0.08; $R^2$: 0.03). Nevertheless, a correlation
between $\Omega_A$ and $O_2$ exists in the Northern St. Lawrence (*p-value*:
< 0.01; $R^2$: 0.49), but not in the Southern St. Lawrence (*p-value*: 0.85;
$R^2$: < 0.01). Furthermore, the correlation observed in the north between $\Omega_A$
and $O_2$ is especially strong when deep Channels (*Deep* model: *p-value*:
< 0.01; $O_2$: 0.20; $R^2$: 0.97) are separated from shallower regions
(*Shallow* model: *p-value*: < 0.01; $O_2$: 0.07; $R^2$: 0.96), with $\Omega_A$
increasing more steeply with increasing $O_2$ in deep Channels. This stronger
correlation is likely caused by the lack of gas exchange with the atmosphere
or the surface mixed layer and the importance of metabolic $CO_2$ in deep
waters, some of which may have mean ages of up to 20 years [@mucci2011]. In the
Northern Gulf, the acidification is following
depth and distance from the Cabot Strait along the Laurentian, Anticosti and
Esquiman Channels due to the progressive oxygen depletion and metabolic carbon
dioxide accumulation [@mucci2011]. There are likely different dynamics at play
in the Southern Gulf, such as the accumulation of metabolic carbon dioxide
produced by rapid oxic degradation of organic matter in the sandy and permeable
sediments of the Magdalen Shelf [*personal communication?*]. <!-- see with Michel -->

We thus divided the analyses between the Southern and Northern St. Lawrence.
The St. Lawrence was divided using the 350m isobath on the southern
slope of the Laurentian Channel, from the Cabot Strait to the tip of the Gaspé
Peninsula. $\Omega_A$ distribution in the Southern St. Lawrence was modelled using the exponential
kriging model.

We predicted $\Omega_A$ using $O_2$ for the Northern St. Lawrence. Whereas
there are few published datasets on $\Omega_{A}$ in the St.
Lawrence, there is a robust time-series on oxygen concentration in the water
column from the Department of Fisheries and Oceans’ (DFO) Atlantic Zone
Monitoring Program [AZMP; @galbraith2018]. We used oxygen concentration data
collected between 2013 and 2017
[@blais2018] and interpolated oxygen % saturation using cokriging with depth as a
covariable, as done in [@dutil2011]. Bathymetric data come from @dutil2011
and have a 100 $km^2$ resolution. For more details, refer to the hypoxia
description. The *Deep* model was used to transform $O_2$ values to $\Omega_A$
in grid cells with depth > 350m, while the *Shallow* model was
applied to cells with depth < 350m.

Based on the wide range of $\Omega_A$ levels at which organism are negatively
affected (see above), we built an index of acidification stress ($A_s$)
ranging between 0 and 1 that slowly begins increasing as $\Omega_A$ $\approx$
$2$, increases more rapidly close to $\Omega_A$ $= 1$ and reaches its peak at
$\Omega_A$ $\approx$ $0.5$:

$$A_s = \frac{-3}{.99 + e^{-2 * \Omega_A}} + 3$$

Hence, the higher the acidification stress, the higher the index of
acidification becomes.

@@

The data used to characterize hypoxia uses oxygen saturation in % and come from
the Department of Fisheries and Oceans’ (DFO) Atlantic Zone Monitoring Program
[AZMP; @galbraith2018] surveys in late spring and fall, as well as from annual
DFO’s multispecies surveys for the northern Gulf in August and for the Magdalen
Shallows in September. We provide a brief summary of data and methods to
characterize hypoxia in this document. For more details, refer to @blais2018.

Oxygen concentration is measured at every station using an oxygen probe
(Sea-Bird SBE43) mounted on the CTD. The probe is calibrated against seawater
samples that are analyzed by Winkler titration on every cast
[see @blais2018 for calibration procedure]. The data used is the last depth
sampled on the CTD profile, which typically corresponds to ~10m above the
bottom. Oxygen concentration ($\mu M$ $L^{-1}$) is converted to oxygen
saturation taking into account the salinity and temperature at the selected
depth.

We interpolated oxygen saturation using cokriging with depth as a covariable,
as done in [@dutil2011]. Bathymetric data come from @dutil2011 and have a
100 $km^2$ resolution.   According to @diaz1995, severe hypoxia can be observed
when dissolved oxygen falls below 2 $ml$ $L^{-1}$, which corresponds to 62.5
$\mu mol$ $L^{-1}$ and ~20% saturation. This is considered as the level
necessary to maintain most animal life. Similarly, @chabot2008 studied the
effects of hypoxia on the energy budget of cod in the St. Lawrence and found
that behavioural effects began manifesting below 70% oxygen saturation and that
survival becomes jeopardised below ~20% saturation. We used these observations
to create an index of hypoxia using an inverted logistic curve that slowly
increases below 70% oxygen saturation, increases acutely as it approaches the
20% oxygen saturation threshold and reaches its peak intensity between 20 and
30% oxygen saturation:

$$H_s = \frac{-1}{.99 + 200 * e^{-0.15 * O_2}} + 1$$

Hence, the higher the hypoxic stress, the higher the index of hypoxia becomes.

@@

The data used to characterize bottom temperature anomalies come from the
Department of Fisheries and Oceans’ (DFO) Atlantic Zone Monitoring Program
[AZMP; @galbraith2018]. We provide a brief summary of data and methods to
characterize the bottom temperature climatology and anomalies in this document.
For more details, refer to @galbraith2018.

Bottom temperatures are interpolated in the Gulf using
conductivity-temperature-depth (CTD) sampling performed annually through DFO's
multispecies surveys for the northern Gulf in August and for the Magdalen
Shallows in September. Using this sampling survey, temperatures are horizontally
interpolated at each 1 m depth layer on a 2 km resolution grid. Bottom
temperatures are then extracted by using a bathymetry layer from the Canadian
Hydrographic Survey [@dutil2012] and selecting the interpolated temperature
from the layer corresponding to the bottom depth at each grid point.

We used temperature anomalies, *i.e.* deviations from long-term normal
conditions, to measure an annual index of stress associated with extreme
temperatures between 2013 and 2017. Temperature anomalies were calculated using
the difference between grid cell values with 1981-2010 climatological averages.
Anomaly time series were normalized by their standard deviation (SD) to allow
comparison between areas of the St. Lawrence with different temperature ranges.
For example, temperatures observed in deep channels are less variable than in
shallower regions of the St. Lawrence. Hence, if anomalies were expressed in
degrees Celsius, it would underestimate the relative importance of anomalies
in deep channels when compared to shallower regions. Grid cells whose monthly
value exceeded ±0.5 standard deviation (SD) from the long-term average were
considered as anomalous [@galbraith2018]. Outliers in the data were defined as
those that fell beyond the interquartile range * 3, identified as extreme
outliers by @tukey1977. Outlier values were capped to correspond to the 5th and
95th percentiles. Anomalies were divided into positive and negative anomalies
and the absolute value of anomalies were used as an indicator of the intensity
of bottom temperature anomalies. The mean anomaly intensity between 2013 and
2017 for each grid cell was used to generate the final index of bottom
temperature anomalies.

@@

The data used to characterize surface temperature anomalies come from the
Department of Fisheries and Oceans’ (DFO) Atlantic Zone Monitoring Program
[AZMP; @galbraith2018]. We provide a brief summary of data and methods to
characterize the surface temperature climatology and anomalies in this document.
For more details, refer to @galbraith2018.

The surface layer is characterized using sea surface temperature (SST) monthly
composites from Advanced Very High Resolution Radiometer (AVHRR) satellite
images obtained from the National Oceanic and Atmospheric Administration (NOAA)
and European Organisation for the Exploitation of Meteorological Satellites
(EUMETSAT). Images used are from DFO’s Maurice Lamontagne Institute at a 1 km
resolution from 1985-2013 and from DFO’s Bedford Institute of Oceanography (BIO)
Operational Remote Sensing group at a 1.5 km resolution since 2014. Monthly
anomalies were constructed as the difference between monthly averages and the
1985-2010 climatological mean for each month.

Surface temperature anomalies were characterized following the same method used
for bottom temperature anomalies. Only the months of May to November were
included to avoid biases associated with the presence of ice cover. Monthly
anomalies from May to November values were summed to obtain an indicator of
annual surface temperature anomaly intensity in each grid cell. The mean
anomaly intensity between 2013 and 2017 for each grid cell was used to generate
the final index of surface temperature anomalies.

@@

- Coastal development
- Direct human impact
- All fisheries data
- Hypoxia
- Inorganic pollution
- Invasive species
- Nutrient pollution
- Organic pollution
- Sea bottom temperature anomalies <!-- verify -->
- Shipping

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/drHist.png}
\caption{Frequency distribution of the untransformed data for all driver layers.}
\label{hist}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics{./Figures/drivers.png}
\caption{Distribution and intensity of transformed and normalized drivers in the Estuary and Gulf of St. Lawrence available on *eDrivers*.}
\label{drivers}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/marimekko.png}
\caption{Frequency distribution of cumulative exposure (*i.e.* sum of normalized driver intensity in each grid cell) and percent contribution of each driver to the frequency distribution of cumulative exposure in the Estuary and Gulf of St. Lawrence.}
\label{marimekko}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/validation.png}
\caption{Validation procedure for the *k-medoids* and *k-means* clustering algorithms based on the number of cluster that maximizes average silhouette width [upper panels; @kaufman1990] and minimizes the total within-cluster sum of squares (WSS; lower panels).}
\label{valid}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics{./Figures/clusterComp.png}
\caption{Comparison of the distribution of the 6 clusters identified using the *k-medoids* and *k-means* clustering algoriths and the percent grid cell correspondance between the two approaches.}
\label{comparison}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/interDissimilarity.png}
\caption{Evaluation of inter-cluster dissimilarity using a similarity percentage analysis (SIMPER) with Bray-Curtis dissimilarity [@clarke1993]. The figure diagonal presents the distribution of the 6 clusters identified using the *k-medoids* clustering algorithm. The lower triangle shows all combinations of inter-cluster dissimilarity with circular barplots showing the percent contribution to total dissimilarity of each driver and with the total inter-cluster dissimilarity in the center of the barplots. The upper triangle shows the average relative intensity of each driver for all driver combinations, with barplots to the left and the right representing the row and columns clusters, respectively.}
\label{inter}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/intraSimilarity.png}
\caption{Evaluation of intra-cluster similarity using the Bray-Curtis similarity index. The distribution of all 7 clusters is presented along with circular barplots showing the percent contribution to total similarity of each driver and with the total intra-cluster similarity in the center of the barplots.}
\label{intra}
\end{figure}
